Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses

### 2013-05-31 masters/body/_region_.tex
so much

\message{ !name(masters.tex) !offset(135) }
\subsection{Geometry Partitioning}
\label{sec:geometryPartioning}
In order to effectively texture a 3D model, we first divide the model
into a set of regions, each to be textured independently. The purpose
of this is to ensure texture continuity along large uniform areas,
while allowing texture boundaries to fall along natural environmental
boundaries. Because textures may not match at such boundaries where
two regions meet, it is important to minimize the visibility of
boundaries. This is done by encouraging region boundaries to occur at
large sharp corners, where texture continuity is less important.

When working with low-resolution models, where surfaces generally
correspond to large planar features such as walls, ceilings, or
floors, and often meet at right angles, each planar surface in the
model is directly treated as a distinct region and textured
separately.

When working with a high-resolution model however, geometry often
represents large features as well as small details found in furniture,
plants, and other miscellaneous objects. For instance, in Figure
\ref{fig:deskGeom}, the geometry modeling the desk and binders
consists of many small triangles at various orientations. Texturing
each of these triangles independently makes little sense, as the
textures applied to each should match up well with the textures of its
neighbors in order to avoid any breaks in the overall image of the
desk and binders. On the other hand, the textures for the triangles
belonging to the wall behind need not match up with the textures on
the desk and binders, and so each group of triangles should be
designated to separate regions. This region grouping is performed by designating all contiguous coplanar groups of triangles as different regions. Any region that is less than $1 m^2$ in size is joined to its largest neighboring region, such that the angle between them is under $90^{\circ}$.

Because a texture is 2D, and the region to be textured may not be
flat, a mapping needs to be defined. We first fit a plane to each
region for the purposes of texturing. This can be accomplished via a
least squares plane-fitting through each triangle vertex, though in
practice we simply use the plane equation of the largest contiguous
section of coplanar triangles, as most regions are characterized by
small outcroppings from a largely planar surface, such as objects on a
table or features protruding from a wall. The 3d vertices within a
region are then projected onto its calculated plane, and the
rectangular bounding box for these projected vertices is
calculated. This bounding box corresponds to the 2D image that will be
created to texture the region.

Of course, the area encompassed by the bounding box is larger than the
corresponding 2d area of the projected geometry, which itself is not
as accurate as the original 3d geometry. Thus, we also create a k-d
tree consisting of the triangle primitives from the original
mesh. Though we generate texture for the 2d bounding box surface, we
will reference the original 3D geometry to ensure accuracy when
texturing.

\message{ !name(masters.tex) !offset(944) }

>>>>

\message{ !name(masters.tex) !offset(938) }
\subsection{Examples}
\label{sec:examples}
As mentioned in Section \ref{sec:dataAcquisition}, the texture mapping
procedure in this thesis can be applied both to low-resolution and
high-resolution models. Low resolution models have an advantage in
their simplicity, and in that only important environmental features
are represented. As a result, images are generated for large sections
of buildings, and boundaries between each texture are minimally
visible. High resolution models have an obvious advantage in terms of
the amount of detail that can be reconstructed, but with poor region
partitioning, as described in Section \ref{sec:geometryPartitioning},
or with high camera pose or geometry reconstruction error, 3D elements
in the environment geometry may not match up well with their imaged
counterparts.

\begin{figure}
  \centering
  \subfloat[][]{
    \includegraphics[width=2in]{results_swarm_3_v.jpg}
    \includegraphics[width=2in]{results_swarm_3_2d.jpg}
    \includegraphics[width=2in]{results_swarm_3_3d.jpg}
  }
  \subfloat[][]{
    \includegraphics[width=2in]{results_swarm_2_v.jpg}
    \includegraphics[width=2in]{results_swarm_2_2d.jpg}
    \includegraphics[width=2in]{results_swarm_2_3d.jpg}
  }
  \subfloat[][]{
    \includegraphics[width=2in]{results_swarm_5_v.jpg}
    \includegraphics[width=2in]{results_swarm_5_2d.jpg}
    \includegraphics[width=2in]{results_swarm_5_3d.jpg}
  }

  \caption{The same indoor environment, as generated using (a) PCA
    plane-fitting, (b) Floor plan extrusion, (c) Watertight mesh
    generation. The first two are low-resolution models, while the
    third is high-resolution}
  \label{fig:modelcomparisons}
\end{figure}

Our approach was tested with three different geometry-reconstruction
methods, a PCA-based plane-fitting method \cite{sanchez2012point}, a
floor plan extrusion method \cite{turnerfloorplan}, and a
voxel-carving mesh generation method \cite{turnerwatertight}. The
first two methods generate lower-resolution models, containing only
major walls, ceilings and floors. The third method generates
high-resolution models, and attempts to reconstruct all scanned
objects in the environment. A comparison of all three methods as
applied to the same dataset is shown in Figure
\ref{fig:modelcomparisons}

\begin{figure}
  \centering
  \caption{low resolution stuff. (a) is not watertight}
  \label{fig:lowresmodels}
\end{figure}

The PCA and floor plan methods produce models at a similar level of
detail. As visible in Figure \ref{fig:lowresmodels}(a), the PCA method
is not watertight, while the floor plan method is. As a result, the
PCA-generated model contains holes where surfaces were not adequately
scanned. On the other hand, the watertight floor plan model sometimes
must make assumptions about the location of surfaces that were not
adequately scanned, in order to maintain watertightness. Because
buildings generally follow straight lines and right angle corners
however, such assumptions tend to be correct. Additionally, the
floor-plan method is generally superior at reconstructing smaller
surfaces, such as small walls, or to approximate curved surfaces,
while the PCA method only fits large planes, and fails in both
cases. As a result, the floor-plan method usually produces more
visually pleasing low-resolution models, and is the method of choice
for generating textured low-resolution models.

\begin{figure}
  \caption{2d vs 3d}
  \label{fig:2dvs3d}
\end{figure}

High-resolution models, as generated by the voxel-carving method, can
produce more accurate reconstructions of environment geometry. With
such models, region partitioning, as described in Section
\ref{sec:geometryPartitioning}, plays an important factor in the
quality of generated textures. If regions are small, boundaries
between adjacent textures become visible, and since each region is
processed independently, image alignment procedures are performed
across smaller areas. If regions are large, then the difference
between the 3D surface geometry and the approximated 2D texturing
surface become large as well, introducing greater texture projection
error. Additionally, in areas where pose error or surface
reconstruction error is high, 3D objects in images do not get
accurately projected onto their modeled counterparts. While large
objects can be aligned to geometry via the methods in Section
\ref{sec:geometryAlignment}, smaller objects such as plants or
computers are difficult to line up to geometry references. While the
compositing techniques is Section \ref{sec:imageCompositing} can
ensure that textures for small objects appear seamless, such textures
may not map accurately upon their corresponding geometry, leading to
visually obvious discrepancies in the textured model. Figure
\ref{fig:2dvs3d} demonstrates this by showcasing the low-resolution
floor plan approach alongside the high-resolution voxel-carving
approach.

As visible in Figure \ref{fig:2dvs3d} and other images in this
section, 2D models using the floor plan approach are generally
preferred, as they provide enough detail in geometry to reconstruct
the basic layout of an environment, while textures can be used to
visualize smaller details. On the other hand, for applications where
furniture and smaller interior details are important, applying
textures to the 3D voxel-carved models provides useful image-based
context for visualizing indoor areas. Figures 1-3 demonstrate further
interior and exterior views of a number of 2D models, while Figures
4-6 demonstrate interior and exterior views of 3D models.

\message{ !name(masters.tex) !offset(1065) }
